Software Ticket Quality

### 2017-11-26 proposal/mprop.tex
Finish data quality section

Another important area of data quality is what methodologies or techniques can 
be applied by organizations in order to improve DQ. There are several studies 
that tried to propose such methodologies. A general overview of such techniques 
was presented by \citet{pipino2002data} - they wanted to present ways of 
developing usable  data quality methods that organizations can implement in 
their own internal processes. After reviewing various techniques of assessing 
data quality in information systems, they reached the conclusion that there is 
no universal approach to assess data quality as it heavily depends on the 
context where it is analysed.

@@

However, there are other aspects that can be investigated when trying to measure
data quality. For example, \citet{prybutok2008evaluating} tried to find if 
leadership and information quality can lead to positive outcomes in an 
e-government's data quality. They conducted a web survey to gather data and test 
their hypotheses. Afterwards, they assessed the City of Denton's e-government 
initiatives, including current plans and implementations. They learned that the 
MBNQA leadership triad (leadership, strategic planning and customer/market focus) 
had a positive impact on the IT quality triad (information, system and service 
quality). Moreover, they found out that both leadership and IT quality improved 
the benefits.

\textbf{Knowing-Why about Data Processes and Data Quality}\cite{lee2003knowing}:
\begin{itemize}
  \item \textbf{What were the goals?}
    They tried to investigate whether knowing-why affects work performance and
    whether knowledge held by people in different roles affect the overall work
    performance. 
  \item \textbf{What was the method?}
    They had 6 companies that served as data collection points. In all of them,
    the research focused on the quality of their customer activity data, tuned
    for the specific domain the company was activating in. They held 2 sessions
    at each company: in the first session, the participants were presented with
    an overview of the research and a questionnaire, while during the second 
    session provided summary feedback on the questionnaire results and gave the
    participants the chance to provide comments and explanations.
  \item \textbf{What did they learn?}
    The major finding of the study was that there is vast complexity of knowledge at work in data production process. 
  \item \textbf{Relevance to our work}: an important research on how knowledge in
    different roles in a company can lead to decreased data quality overall. It
    will help us to analyse the software tickets we will mine better.
\end{itemize}

\textbf{Antecedents of Information and System Quality}
\cite{nelson2005antecedents}:
\begin{itemize}
  \item \textbf{What were the goals?}
    The authors had 2 main research objectives they wanted to aim for in this
    paper:
      \begin{itemize}
        \item identify a set of antecedents that both drive information and
          system quality, as well as define the nature of the IT artifact;
        \item explore data warehousing in general, especially analytical tools,
          predefined reports and ad hoc queries.
        \end{itemize}
  \item \textbf{What was the method?}
    They conducted a cross-functional survey to test the model the authors 
    proposed. They focused on user experience with a data warehouse. They sent
    email invites to the Data Warehouse Institute which distributed it further
    to organizations, among which 7 agreed to participate, yielding a total of
    465 completed surveys. 
  \item \textbf{What did they learn?}
    They learned that their selected features were indeed a good indicator of
    overall information and system quality. They also found out that accuracy is
    the dominant determinant across all three data warehouse technologies, 
    followed by completeness and format. Also, the results showed that more 
    attention needs to be given to differences across varying technologies. 
  \item \textbf{Relevance to our work}: this paper presents important findings
    regarding information and system quality in an IT environment. We can use it
    when analysing the quality of the tickets we will mine.
\end{itemize}

\textbf{Organizational Impact of Information Quality}
\cite{gorla2010organizational}:
\begin{itemize}
  \item \textbf{What were the goals?}
    The authors had two main research questions they wanted to address:
      \begin{itemize}
        \item what individual/combined influences system quality, service 
          quality, information quality have on organizational impact?
        \item what effect does system quality have on information quality?
      \end{itemize}
  \item \textbf{What was the method?}
    They conducted a construct measurement for the IS quality dimensions and 
    collected data through empirical testing.
  \item \textbf{What did they learn?}
    Firstly, they learned that service quality has the greatest impact 
    of all three quality constructs. Moreover, they found out that there is a 
    linkage between system and information quality, fact that previous research
    did not reveal. Lastly, their results indicate that the above-mentioned 
    quality dimensions have a significant positive influence on organizational
    impact either directly or indirectly.
  \item \textbf{Relevance to our work}: the paper can provide us insights into
    how valuable information quality is and what an impact it can have.
\end{itemize}

\textbf{Impact of Poor Data Quality}\cite{redman1998impact}:
\begin{itemize}
  \item \textbf{What were the goals?}
    The main purpose of the article is to provide some insights into how
    data quality can have a major economical impact on a company, as well
    as to raise awareness about this issue.
  \item \textbf{What was the method?}
    The author has analysed various large enterprises and their available data 
    to infer conclusions about the impact data quality has.
  \item \textbf{What did they learn?}
    There are three main issues across most enterprises:
      \begin{itemize}
        \item inaccurate data;
        \item inconsistencies across databases;
        \item unavailable data necessary for certain operations.
      \end{itemize}
    Moreover, the paper also presents a list of impacts poor data quality brings, among 
    which we can find:
      \begin{itemize}
        \item lowered customer satisfaction;
        \item increased cost;
        \item lowered employee satisfaction;
        \item it becomes more difficult to set strategy;
        \item poorer decision making.
      \end{itemize}
  \item \textbf{Relevance to our work}: this is a key paper on data quality in
    an enterprise setting and what impact it can have. It is valuable to our research 
    because we can relate the findings with what negative impacts poor tickets
    can bring to software projects.
\end{itemize}

>>>>

\citet{nelson2005antecedents} proposed another technique for measuring data 
quality in an organization by, firstly, setting 2 main research questions:
  \begin{itemize}
    \item identify a set of antecedents that both drive information and
      system quality, as well as define the nature of the IT artifact;
    \item explore data warehousing in general, especially analytical tools,
      predefined reports and ad hoc queries.
  \end{itemize}

Then, the authors set up a model to define a tree-structured representation
of system quality and data quality, as follows:
  \begin{itemize}
    \item data quality - defined by completeness, accuracy, format and currency;
    \item system quality - defined by reliability, flexibility, integration,
    response time and accessibility;
    \item then, data and systems available are evaluated to infer 
    data satisfaction and system satisfaction (coming from customers), which
    in turn will compute the final satisfaction score of the product.
  \end{itemize}

After conducting a cross-functional survey to test the model, they learned that
the features they selected were a good indicator of overall information/data and
system quality. They also found that accuracy is the dominant determinant across
all three data warehouse technologies, followed by completeness and format. Last
but not least, another discovery was that more attention needs to be given to
differences across varying technologies.

Another important area of data quality is what methodologies or techniques can 
be applied by organizations in order to improve data quality. 
There are several studies that tried to propose such methodologies. A general 
overview of such techniques  was presented by \citet{pipino2002data} - they 
wanted to present ways of developing usable  data quality methods that 
organizations can implement in their own internal processes. After reviewing 
various techniques of assessing data quality in information systems, they reached 
the conclusion that there is no universal approach to assess data quality as it  
heavily depends on the context where it is analysed.

@@

However, there are other aspects that can be investigated when trying to improve
data quality. For example, \citet{prybutok2008evaluating} tried to find if 
leadership and information quality can lead to positive outcomes in an 
e-government's data quality. They conducted a web survey to gather data and test 
their hypotheses. Afterwards, they assessed the City of Denton's e-government 
initiatives, including current plans and implementations. They learned that the 
MBNQA leadership triad (leadership, strategic planning and customer/market focus) 
had a positive impact on the IT quality triad (information, system and service 
quality). Moreover, they found out that both leadership and IT quality improved 
the benefits.

Finally, after defining, measuring and improving data quality, we also need
to be able to assess the impact poor DQ has on a company. In this area, there
are several authors that investigated various implications of low indices
of data quality.

One such research is the one done by \citet{gorla2010organizational}. They wanted
to examine what influences do system quality, service quality and data quality
have on an organization, as well as what effect does system quality have on
data quality. After conducting a construct measurement for the information
systems quality dimensions \citep{swanson1997maintaining} and collecting data
through empirical testing, they learned that service quality has the greatest
impact of all three quality constructs. Moreover, they found out that there is 
a linkage between system and information quality, fact that previous research
did not reveal. Last but not least, their results indicate that the 
above-mentioned quality dimensions have a significant positive influence on 
organizational impact either directly or indirectly.

On the other hand, \citet{redman1998impact} had different findings. Even though
they did not analyze multiple types of quality, but only data quality, they 
learned that there are three main issues across most enterprises: inaccurate
data, inconsistencies across databases and unavailable data necessary for 
certain operations. Furthermore, they presented a number of impacts that
poor data quality has on enterprises: lowered customer satisfaction, increased
cost, lowered employee satisfaction, it becomes more difficult to set strategy,
as well as worse decision making.

Another research, the one of \citet{lee2003knowing}, investigated another 
aspect: whether knowing-why affects work performance and whether knowledge held
by people in different roles affect the overall work performance. After
conducting various surveys with 6 companies that served as data collection 
points, they reached the conclusion that there is vast complexity of 
knowledge at work in the data production process and if these gaps are not 
bridged it might lead to decrased data quality.
